---
title       : Slidify Presentation
subtitle    : 
author      : Andrew Kryzanek
job         : Senior Seminar 3/3/14
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}


---

## Basics

1. Edit YAML front matter - a human reaadable data serialization format that takes concepts from programming languages such as C, Perl, and Python, and ideas from KML and the data format of eletctronic mail
(YAML is a recursive acronym for "YAML Ain't Markup Language" and used to mean "Yet Another Markup Language.")

2. Write using R Markdown

3. Use an empty line followed by three dashes to separate slides!

--- .class #id 
## Installation

Step  Description	Code
- require(devtools)
- install_github("slidify","ramnathv")
- install_github("slidifyLibraries", "ramnathv")
- library(slidify)
- author("mydeck")

Then edit in RMarkdown

- slidify("index.RMD")
- publish(user = "USER", repo = "REPO")

---

```{r results ='hide', echo=FALSE}
require(class)
require(datasets)
require(devtools)
require(e1071)
require(lattice)
require(maps)
require(MASS)
require(methods)
require(PASWR)
require(PASWR2)
require(ggplot2)
require(graphics)
require(grDevices)
require(stats)
require(utils)
```

---
## Uses Code-Chunks

```{r echo = TRUE}


summary(HSwrestler)

```

---
```{r echo = TRUE}
x <- glm(HSwrestler$HT~ HSwrestler$WT+HSwrestler$TANFAT+HSwrestler$SKFAT)
summary(x)
```
---
```{r echo = TRUE}
hist(HSwrestler$WT, col = "blue")
```
---
```{r echo = TRUE}
boxplot(HT~WT, data=HSwrestler, main="Size Distribution")
```
